Adaptive Scheduling of Scientific Workflows

### 2024-04-22 main.tex
corrected the blc definition

 HEFTM-BLC: from the study of the fork (see below), it seems important
 to also account for the size of the data as input of a task,
 to give more priority at tasks with potential large incoming communications.
 For each task, we compute its modified bottom level: 
 $$blc(u) = bl(u) + \max_{(v,u)\in E} c_{v,u}   . $$

>>>>

 HEFTM-BLC: from the study of the fork (see below), it seems important
 to also account for the size of the data as input of a task,
 to give more priority at tasks with potential large incoming communications.
 For each task, we compute its modified bottom level: 
 $$blc(u) = w_u + \max_{(u,w)\in E} \{c_{u,w} + blc(w)\} + \max_{(v,u)\in E} c_{v,u}   . $$

    \skug{avoid having mixed ranks, when the memory size of the lower task is not taken into account}
